Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-06-02 paper/main.tex
astro-ph version

There is a long observational tradition studying galactic properties
as a function of their large scale environment
\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}. In
these situations the environment definition is usually based on
quantities easily accessible to observations such as local number
density or nearest neighbour measurements. With
the advent of large surveys the visibility of the cosmic web became
clear. As a consequence, in order to capture its filamentarity, the
environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed dark
matter density/velocity field
\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014},
including recent developments that take into account the rotational
part of the velocity field \citep[e.g.][]{Wang2013,LibeskindVorticity}.

@@

\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Along &
Alignment & Mass dependence\\\hline

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1 \hMpc$ &
$\hat{e}_3$ (filament) &$++$ & $>10^{12}$\hMsun\\
&   & &
$\hat{e}_3$ (filament) & $+$ & $<10^{12}$\hMsun\\

@@

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ &
$\hat{e}_3$ (filament) &$--$ & $>10^{12}$\hMsun\\
&   & &
$\hat{e}_3$ (filament) & none & $<10^{12}$\hMsun\\
&   & &
$\hat{e}_1$ (wall) & $--$ & $>10^{12}$\hMsun\\

@@

\cite{Libeskind2013} & V-Web & $1 \hMpc$ &
filament &$++$ & $>10^{12}$\hMsun\\
&   & &
filament &$+$ & $<10^{12}$\hMsun\\
&   & &
wall & $++$ & all masses\\\hline

\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc &
filament & $++$ & $>10^{12}\hMsun$\\

@@

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ &
$\hat{e}_3$  (filament) & - & $>10^{12}$\hMsun\\

@@

We thank Kristin Riebe for her work to make the cosmic-web data available in the Multidark database.

>>>>

There is a long observational tradition studying galactic properties
as a function of their large scale environment
\citep[e.g.][]{Oemler1974,Dressler1980,Pimbblet2002,Gomez2003,Kauffmann2004,Abbas2006,Baldry2006,Park2007,OMill2008,Gonzalez2009,Padilla2010,Wilman2010,Muldrew2012}. In
these situations the environment definition is usually based on
quantities easily accessible to observations such as local number
density or nearest neighbour measurements. With
the advent of large galaxy surveys and cosmological N-body simulations
the visibility of the cosmic web and its physical origin became
clear. As a consequence, in order to capture its filamentarity, the
environment definition started to be more complex, involving shear and gradient properties of the galaxy density field or the reconstructed/simulated dark
matter density/velocity field
\citep[e.g.][]{Lee2005,AragonCalvo2007,Hahn2007,Sousbie2008,Zhang2009,Tweb,MunozCuartas2011,Vweb,Trowland2013,Tempel2014},
including recent developments that take into account the rotational
part of the velocity field \citep[e.g.][]{Wang2013,LibeskindVorticity}.

@@

\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Along &
Alignment & Mass dependence\\
 & & ($\hMpc$)& & & \\\hline

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ &
$\hat{e}_3$ (filament) &$++$ & $>10^{12}$\hMsun\\
&   & &
$\hat{e}_3$ (filament) & $+$ & $<10^{12}$\hMsun\\

@@

{\bf Forero-Romero et al. (2014)} & Vp-Web & $0.5-1$ &
$\hat{e}_3$ (filament) &$--$ & $>10^{12}$\hMsun\\
&   & &
$\hat{e}_3$ (filament) & none & $<10^{12}$\hMsun\\
&   & &
$\hat{e}_1$ (wall) & $--$ & $>10^{12}$\hMsun\\

@@

\cite{Libeskind2013} & V-Web & $1$ &
filament &$++$ & $>10^{12}$\hMsun\\
&   & &
filament &$+$ & $<10^{12}$\hMsun\\
&   & &
wall & $++$ & all masses\\\hline

\cite{Zhang2009}  & Hessian density field &  $2.1$ &
filament & $++$ & $>10^{12}\hMsun$\\

@@

{\bf Forero-Romero et al. (2014)} & T-Web & $0.5-1$ &
$\hat{e}_3$  (filament) & $-$ & $>10^{12}$\hMsun\\

@@

We thank Kristin Riebe for her work to make the cosmic web data available in the Multidark database.
